Self Regulation Ontology Retest Data Report

### 2017-11-16 code/SRO_Report.Rmd
cleaning up report

### Histograms of reliability metrics (point estimates)

@@

# rel_df %>%
#   select(dv, task, spearman, pearson, icc) %>%
#   gather(key, value, -dv, -task) %>%
#   ggplot(aes(value, fill=task))+
#   geom_histogram(alpha = 0.5, position = 'identity')+
#   facet_wrap(~key)+
#   theme_bw()+
#   theme(legend.position = 'bottom',
#         legend.title = element_blank())+
#   xlab("")

@@

### Relationship between reliability metrics (point estimates)

```{r warning=FALSE, message=FALSE}
p1 = rel_df %>%
  ggplot(aes(spearman, icc, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none")+
  geom_abline(intercept = 0, slope=1)

p2 = rel_df %>%
  ggplot(aes(pearson, icc, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none")+
  geom_abline(intercept = 0, slope=1)

p3 = rel_df %>%
  ggplot(aes(pearson, spearman, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none")+
  geom_abline(intercept = 0, slope=1)

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            num_measures = n(),
            num_trials = unique(num_all_trials)) %>%
  arrange(-median_icc, -median_spearman)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
```

>>>>

### Histograms of reliability metrics

@@

@@

### Relationship between reliability metrics

```{r warning=FALSE, message=FALSE}
p1 = boot_df %>%
  ggplot(aes(spearman, icc, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none")+
  geom_abline(intercept = 0, slope=1)

p2 = boot_df %>%
  ggplot(aes(pearson, icc, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none")+
  geom_abline(intercept = 0, slope=1)

p3 = boot_df %>%
  ggplot(aes(pearson, spearman, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank(),
        legend.position = "none")+
  geom_abline(intercept = 0, slope=1)

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n(),
            num_trials = unique(num_all_trials))%>%
  arrange(-median_icc, -median_spearman)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc',
                        'min_spearman', 'min_icc',
                        'max_spearman', 'max_icc'), digits=3)
```
